\section{Introduction}
ACME (Aston Car Management Enterprises) is a car rental that offers rentals, primarily but not exclusively, to people in the Aston area.
This includes a range of customers from working individuals to the large student population the city has. The company currently uses email and telephone
for both customer requests and internal communications. 

However the company has realised that the current system is outdated and not a good user experience for the customer. In addition to this the 
profits of the company have been on a slow decline as newer competition has risen, taking away some of ACMEs customer base. 

The aim of this report is to come up with ways in which this problem can be tackled, coming up with a design that can be implemented. This report
discuss the stakeholders, business goals and current situation ACME is in. From this use cases and requirements will for the new system will be designed,
followed by both activity and sequence diagrams to demonstrate how the system could work on a lower level. Finally the report will evaluate the suggested
design, offering additional changes that could be made in the future.

The features on the system I will be focusing on in this report will be:
\begin{itemize}
  \item Adding customer information
  \item Taking payment
  \item Handling the return of a vehicle
  \item Starting a new hire
  \item Adding a new car to the system
\end{itemize}

Currently ACME uses an outdated paper-based approach, communicating with customers and other staff members using a combination of telephone and email.
The current system has numerous problems such as: 
\begin{enumerate}
  \item Due to the paper-based approach important details such as details about orders, cars and accounting can often go missing causing issues 
  for both customers and internal staff.
  \item Backups of data are difficult and time consuming due to the paper-based approach and their risk management for the same reason is near non-existent.
  \item Customer experience is not optimal due to the updates coming through telephone calls or email only.
\end{enumerate}

\vspace{0.2cm}

I have used plantuml [1] and LaTeX [2] to create this document. All source code can be found in this
\href{https://github.com/OMBowkerBBC/DC4600-Assignment1}{\textbf{github repository}}.

\newpage
