\section{References}

\noindent [1] PlantUML. (2023) \textit{PlantUML in a nutshell} [online]. Available at \url{https://plantuml.com/} (accessed on 28th May 2023).
\vspace{0.2cm}

\noindent [2] LaTeX. (2023) \textit{The LaTeX project} [online]. Available at \url{https://www.latex-project.org/} (accessed on 28th May 2023).
\vspace{0.2cm}

\noindent [3] Statista. (2023) \textit{Crypto ownership by country 2019-2023 | Statista} [online]. Available at \url{https://www.statista.com/statistics/1202468/global-cryptocurrency-ownership/} (accessed on 28th May 2023).
\vspace{0.2cm}

\noindent [4] Best, R. (2021) \textit{Cryptocurrency adoption among consumers - statistics \& facts | Statista} [online]. Available at \url{https://www.statista.com/topics/7705/cryptocurrency-adoption-among-consumers/#topicOverview} (accessed on 28th May 2023).
\vspace{0.2cm}

\noindent [5] Nagari, S. (2023) \textit{Cryptocurrency Adoption Statistics in the UK} [online]. Available at \url{https://www.banklesstimes.com/uk/buy-cryptocurrency/crypto-adoption/} (accessed on 28th May 2023).
\vspace{0.2cm}

\noindent [6] Laoyan, S. (2022) \textit{What is Agile methodology? (A beginner's guide)} [online]. Available at \url{https://asana.com/resources/agile-methodology} (accessed on 29th May).
\vspace{0.2cm}

\noindent [7] Arkbauer. (2023) \textit{Software development life-cycle (SDLC)} [online]. Available at \url{https://arkbauer.com/blog/software-development-life-cycle-sdlc/} (accessed on 29th May).
\vspace{0.2cm}

\noindent [8] Coursera. (2023) \textit{What Is the Software Development Life Cycle? SDLC Explained} [online]. Available at \url{https://www.coursera.org/articles/software-development-life-cycle} (accessed on 29th May).
\vspace{0.2cm}

\noindent [9] Atlassian. (2023) \textit{What is the Agile methodology?} [online]. Available at \url{https://www.atlassian.com/agile} (accessed on 29th May).
\vspace{0.2cm}

\noindent [10] Cunningham, W. (2001) \textit{Manifesto for Agile Software Development} [online]. Available at \url{https://agilemanifesto.org/iso/en/manifesto.html} (accessed on 29th May).
\vspace{0.2cm}

\noindent [11] University of Minnesota. (2022) \textit{Agile Methodology: Advantages and Disadvantages} [online]. Available at \url{https://ccaps.umn.edu/story/agile-methodology-advantages-and-disadvantages} (accessed on 29th May).
\vspace{0.2cm}

\noindent [12] anthillsoftwareleeds. (2021) \textit{Why Collaboration Is Key To Customer Satisfaction} [online]. Available at \url{https://anthill.co.uk/insights/why-collaboration-is-key-to-customer-satisfaction/} (accessed on 29th May).
\vspace{0.2cm}

\noindent [13] Sommerville, I. (2016). Software Engineering. Tenth edition. USA:Pearson.
\vspace{0.2cm}

\noindent [14] Miles, R., Hamilton, K. (2006). Learning UML 2.0. USA:O'Reilly.
\vspace{0.2cm}

\noindent [15] Stripe, Inc. (2023) \textit{Stripe | Payment Processing Platform for the Internet} [online]. Available at \url{https://stripe.com/gb} (accessed on 29th May).
\vspace{0.2cm}

\noindent [16] L, Georgieva. (2021) \textit{Digital Inclusion and the Elderly: The Case of Online Banking} [online]. Available at \url{http://lrec-conf.org/workshops/lrec2018/W14/pdf/2_W14.pdf} (accessed on 29th May).
\vspace{0.2cm}

\noindent [17] Glassdoor. (2023) \textit{Salary: Software Developer in United Kingdom 2023 | Glassdoor} [online]. Available at \url{https://www.glassdoor.co.uk/Salaries/software-developer-salary-SRCH_KO0,18.htm} (accessed on 8th June)
\vspace{0.2cm}

\noindent [18] Ashmore, s. (2014). Introduction to agile methods. USA:Pearson.
\vspace{0.2cm}

\noindent [19] Codecademy Team. (2023) \textit{What is CRUD?} [online]. Available at \url{https://www.codecademy.com/article/what-is-crud} (accessed on 8th June)
\vspace{0.2cm}

\noindent [20] Consensys. (2023) \textit{The crypto wallet for Defi, Web3 Dapps and NFTs | MetaMask} [online]. Available at \url{https://metamask.io/} (accessed on 8th June)
\vspace{0.2cm}

\noindent [21] Meta Platforms Inc. (2023) \textit{React Native · Learn once, write anywhere} [online]. Available at \url{https://reactnative.dev/} (accessed on 8th June)
\vspace{0.2cm}

\noindent [22] Alphabet Inc. (2023) \textit{Flutter - Build apps for any screen} [online]. Available at \url{https://flutter.dev/} (accessed on 8th June)
\vspace{0.2cm}

\noindent [23] Financial Conduct Authority. (2023) \textit{Regulation of Digital Assets in the UK} [online]. Available at \url{https://www.fca.org.uk/news/speeches/regulation-digital-assets-uk} (accessed on 8th June)
\vspace{0.2cm}

\noindent [24] Stripe Inc. (2023) \textit{Stripe API reference - curl} [online]. Available at \url{https://stripe.com/docs/api} (accessed on 8th June)
\vspace{0.2cm}

\newpage
